---
output:
    word_document
---

```{r setup, echo=F, message=F, warning=F, results='hide'}
library(here)

setwd(here::here('analyses'))

renv::activate()

library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyr)

knitr::opts_chunk$set(device = 'png',
                      dpi = 300,
                      echo = F,
                      message = F)

options(scipen = 5,
        digits = 3)

.fine_lim_hrk <- 10200
.fine_lim_usd <- 4500

ggplot2::theme_set(theme_minimal())

source(here('analyses',
            'helpers',
            'helpers_plot.R'))
```

# Analyses

## Study 1a

```{r s1a-load-data}
source(here::here('analyses',
                  'study_1a',
                  'wrangling',
                  'study_1a_prepare-analysis-data.R'))
```

```{r s1a-plot-assessments}
.p_data <- d_s1a %>%
    tidyr::pivot_longer(.,
                        cols = c('assess_fine',
                                 'assess_blame'),
                        names_pattern = 'assess_(\\w+)',
                        names_to = 'assessment',
                        values_to = 'value')


.summary <- dplyr::group_by(.p_data,
                            assessment,
                            experimental_situation) %>%
    dplyr::summarise(.,
                     m = mean(value))

ggplot2::ggplot(.p_data,
                aes(x = experimental_situation,
                    y = value)) +
    ggplot2::facet_wrap('assessment',
                        scales = 'free_y') +
    ggplot2::geom_point(size = 3,
                        alpha = .4,
                        position = ggplot2::position_jitter(width = .25,
                                                            height = 0)) +
    geom_point(inherit.aes = F,
               data = .summary,
               aes(x = experimental_situation,
                   y = m),
               shape = 4,
               stroke = 2,
               size = 5) +
    scale_y_continuous(limits = setLimitsHRK,
                       breaks = setBreaksMajorHRK)
```

The groups that read the agentive and the nonagentive description of the
event were compared on the amount fined and blame level assessment using a
one-sided t-test. Following the findings of the original study, we assumed
that reading the agentive description of the event would lead to a higher
fine and higher assessed blame level; this direction was also posited in the
one-sided t-tests.

## Study 1b

## Study 2a

## Study 2b
