---
output:
    word_document
---

```{r setup, echo=F, message=F, warning=F, results='hide'}
renv::activate(here::here('analyses'))

library(here)
library(dplyr)
library(magrittr)
library(ggplot2)
library(tidyr)
library(knitr)
library(glue)
library(ggdist)
library(ggpubr)

knitr::opts_chunk$set(device = 'png',
                      dpi = 300,
                      echo = F,
                      message = F,
                      fig.width = 8,
                      fig.height = 8 * 9 / 16)

options(scipen = 5,
        digits = 3)

.fine_lim_hrk <- 10200
.fine_lim_usd <- 4500

ggplot2::theme_set(theme_minimal())

ggplot2::theme_update(strip.placement = 'outside',
                      panel.spacing.y = unit(x = 20,
                                             units = 'pt'))

source(here('analyses',
            'helpers',
            'plots.R'))

source(here('analyses',
            'helpers',
            'stats.R'))

source(here('analyses',
            'helpers',
            'tables.R'))
```

# Analyses

## Study 1a

```{r s1a-load-data}
source(here::here('analyses',
                  'study_1a',
                  'wrangling',
                  'study_1a_prepare-analysis-data.R'))
```

```{r s1a-plot-assessments, fig.cap='Individual responses to the proposed fine and stated level of blame (jittered horizontally). The X-es represent each group\'s mean value.'}
.p_data <- d_s1a %>%
    tidyr::pivot_longer(.,
                        cols = c('assess_fine',
                                 'assess_blame'),
                        names_pattern = 'assess_(\\w+)',
                        names_to = 'assessment',
                        values_to = 'value')


.summary <- dplyr::group_by(.p_data,
                            assessment,
                            experimental_situation) %>%
    dplyr::summarise(.,
                     m = mean(value),
                     stdev = sd(value))

. <- filter(.p_data,
       assessment == 'blame') %>%
    group_by(.,
             experimental_situation,
             value) %>%
    summarise(n = n()) %>%
    group_by(experimental_situation) %>%
    summarise(n = max(n))

.summary <- dplyr::left_join(.summary,
                             .,
                             by = 'experimental_situation')

s1Plot(.p_data,
       .summary)
```

The groups that read the agentive and the nonagentive description of the
event were compared on the amount fined and blame level assessment using a
one-sided t-test. Following the findings of the original study, we assumed
that reading the agentive description of the event would lead to a higher
fine and higher assessed blame level; this direction was also posited in the
one-sided t-tests. Also, as a manipulation check, participants were asked to
rate the extent to which the subject of the described event played an active
role in starting the fire. Groups were compared on those assessments using
a two-sided t-test.

```{r s1a-t-test}
t_active <- t.test(assess_active_role ~ experimental_situation,
                   d_s1a,
                   alternative = 'two.sided',
                   var.equal = T,
                   paired = F,
                   confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1a,
                                  'active_role')

d_manip <- getCohenD(.d_groups[[1]],
                     .d_groups[[2]])

t_fine <- t.test(assess_fine ~ experimental_situation,
                 d_s1a,
                 alternative = 'greater',
                 var.equal = T,
                 paired = F,
                 confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1a,
                                  'fine')

d_fine <- getCohenD(.d_groups[[1]],
                    .d_groups[[2]])

t_blame <- t.test(assess_blame ~ experimental_situation,
                  d_s1a,
                  alternative = 'greater',
                  var.equal = T,
                  paired = F,
                  confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1a,
                                  'blame')

d_blame <- getCohenD(.d_groups[[1]],
                     .d_groups[[2]])
```

```{r s1a-table}
s1Table(.summary,
        d_fine,
        d_blame,
        t_fine,
        t_blame)
```

```{r s1a-manip-check-describe}
.summary_manip <- d_s1a %>%
    group_by(.,
             experimental_situation) %>%
    summarise(.,
              m = mean(assess_active_role,
                       na.rm = T),
              stdev = sd(assess_active_role,
                         na.rm = T))
```

Comparing the assessment of the subject's activity,
we obtain a t-test that is significant at the .05 level
($\Delta_{ag-nonag} = `r t_active$estimate[1] - t_active$estimate[2]`,
t(`r t_active$parameter`) = `r t_active$statistic`,
p = `r t_active$p.value`,
95\% \text{CI} = [`r t_active$conf.int[1]`, `r t_active$conf.int[2]`],
d = `r d_manip`$).
The mean assessment of the subject's activity given by the participants who
read the agentive description of the event was
`r filter(.summary_manip, experimental_situation == 'agentive') %>% pull(m)`
(SD = `r filter(.summary_manip, experimental_situation == 'agentive') %>%
pull(stdev)`).
The mean assessment of the subject's activity given by the participants who
read the nonagentive description of the event was
`r filter(.summary_manip, experimental_situation == 'nonagentive') %>% pull(m)`
(SD = `r filter(.summary_manip, experimental_situation == 'nonagentive') %>%
pull(stdev)`).

The mean fine assigned by the participants who read the agentive description
of the event was
`r filter(.summary, assessment == 'fine' &
experimental_situation == 'agentive') %>% pull(m)` HRK
(SD = `r filter(.summary, assessment == 'fine' &
experimental_situation == 'agentive') %>% pull(stdev)`), and the mean fine
assigned by the participants who read the nonagentive description was
`r filter(.summary, assessment == 'fine' &
experimental_situation == 'nonagentive') %>% pull(m)` HRK
(SD = `r filter(.summary, assessment == 'fine' &
experimental_situation == 'nonagentive') %>% pull(stdev)`).
Comparing the amounts fined by the two groups, we obtain a t-test that is not
significant at the .05 level
($\Delta_{ag-nonag} = `r t_fine$estimate[1] - t_fine$estimate[2]` \text{HRK},
t(`r t_fine$parameter`) = `r t_fine$statistic`,
p = `r t_fine$p.value`,
95\% \text{CI} = [`r t_fine$conf.int[1]`, `r t_fine$conf.int[2]`],
d = `r d_fine`$).

The mean level of blame assigned by the participants who read the agentive
description of the event was
`r filter(.summary, assessment == 'blame' &
experimental_situation == 'agentive') %>% pull(m)`
(SD = `r filter(.summary, assessment == 'blame' &
experimental_situation == 'agentive') %>% pull(stdev)`), and the mean blame
assigned by the participants who read the nonagentive description was
`r filter(.summary, assessment == 'blame' &
experimental_situation == 'nonagentive') %>% pull(m)`
(SD = `r filter(.summary, assessment == 'blame' &
experimental_situation == 'nonagentive') %>% pull(stdev)`).
Comparing the level of blame assessed by the two groups, we obtain a t-test
that is significant at the .05 level
($\Delta_{ag-nonag} = `r t_blame$estimate[1] - t_blame$estimate[2]`,
t(`r t_blame$parameter`) = `r t_blame$statistic`,
p = `r t_blame$p.value`,
95\% \text{CI} = [`r t_blame$conf.int[1]`, `r t_blame$conf.int[2]`],
d = `r d_blame`$).

## Study 1b

```{r s1b-load-data}
source(here::here('analyses',
                  'study_1b',
                  'wrangling',
                  'study_1b_prepare-analysis-data.R'))
```

```{r s1b-plot-assessments, fig.cap='Individual responses to the proposed fine and stated level of blame (jittered horizontally). The X-es represent each group\'s mean value.'}
.p_data <- d_s1b %>%
    tidyr::pivot_longer(.,
                        cols = c('assess_fine',
                                 'assess_blame'),
                        names_pattern = 'assess_(\\w+)',
                        names_to = 'assessment',
                        values_to = 'value')


.summary <- dplyr::group_by(.p_data,
                            assessment,
                            experimental_situation) %>%
    dplyr::summarise(.,
                     m = mean(value),
                     stdev = sd(value))

s1Plot(.p_data,
       .summary)
```

The groups that read the agentive and the nonagentive description of the
event were compared on the amount fined and blame level assessment using a
one-sided t-test. Following the findings of the original study, we assumed
that reading the agentive description of the event would lead to a higher
fine and higher assessed blame level; this direction was also posited in the
one-sided t-tests.

```{r s1b-t-test}
t_active <- t.test(assess_active_role ~ experimental_situation,
                   d_s1b,
                   alternative = 'two.sided',
                   var.equal = T,
                   paired = F,
                   confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1b,
                                  'active_role')

d_manip <- getCohenD(.d_groups[[1]],
                     .d_groups[[2]])

t_fine <- t.test(assess_fine ~ experimental_situation,
                 d_s1b,
                 alternative = 'greater',
                 var.equal = T,
                 paired = F,
                 confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1b,
                                  'fine')

d_fine <- getCohenD(.d_groups[[1]],
                    .d_groups[[2]])

t_blame <- t.test(assess_blame ~ experimental_situation,
                  d_s1b,
                  alternative = 'greater',
                  var.equal = T,
                  paired = F,
                  confidence.interval = .95)

.d_groups <- extractCohenDSamples(d_s1b,
                                  'blame')

d_blame <- getCohenD(.d_groups[[1]],
                     .d_groups[[2]])
```

```{r s1b-table}
s1Table(.summary,
        d_fine,
        d_blame,
        t_fine,
        t_blame)
```

```{r s1b-manip-check-describe}
.summary_manip <- d_s1b %>%
    group_by(.,
             experimental_situation) %>%
    summarise(.,
              m = mean(assess_active_role,
                       na.rm = T),
              stdev = sd(assess_active_role,
                         na.rm = T))
```

Comparing the assessment of the subject's activity,
we obtain a t-test that is significant at the .05 level
($\Delta_{ag-nonag} = `r t_active$estimate[1] - t_active$estimate[2]`,
t(`r t_active$parameter`) = `r t_active$statistic`,
p = `r t_active$p.value`,
95\% \text{CI} = [`r t_active$conf.int[1]`, `r t_active$conf.int[2]`],
d = `r d_manip`$).
The mean assessment of the subject's activity given by the participants who
read the agentive description of the event was
`r filter(.summary_manip, experimental_situation == 'agentive') %>% pull(m)`
(SD = `r filter(.summary_manip, experimental_situation == 'agentive') %>%
pull(stdev)`).
The mean assessment of the subject's activity given by the participants who
read the nonagentive description of the event was
`r filter(.summary_manip, experimental_situation == 'nonagentive') %>% pull(m)`
(SD = `r filter(.summary_manip, experimental_situation == 'nonagentive') %>%
pull(stdev)`).

The mean fine assigned by the participants who read the agentive description
of the event was
`r filter(.summary, assessment == 'fine' &
experimental_situation == 'agentive') %>% pull(m)` USD
(SD = `r filter(.summary, assessment == 'fine' &
experimental_situation == 'agentive') %>% pull(stdev)`), and the mean fine
assigned by the participants who read the nonagentive description was
`r filter(.summary, assessment == 'fine' &
experimental_situation == 'nonagentive') %>% pull(m)` USD
(SD = `r filter(.summary, assessment == 'fine' &
experimental_situation == 'nonagentive') %>% pull(stdev)`).
Comparing the amounts fined by the two groups, we obtain a t-test that is
significant at the .05 level
($\Delta_{ag-nonag} = `r t_fine$estimate[1] - t_fine$estimate[2]` \text{USD},
t(`r t_fine$parameter`) = `r t_fine$statistic`,
p = `r t_fine$p.value`,
95\% \text{CI} = [`r t_fine$conf.int[1]`, `r t_fine$conf.int[2]`]$).

The mean level of blame assigned by the participants who read the agentive
description of the event was
`r filter(.summary, assessment == 'blame' &
experimental_situation == 'agentive') %>% pull(m)`
(SD = `r filter(.summary, assessment == 'blame' &
experimental_situation == 'agentive') %>% pull(stdev)`), and the mean blame
assigned by the participants who read the nonagentive description was
`r filter(.summary, assessment == 'blame' &
experimental_situation == 'nonagentive') %>% pull(m)`
(SD = `r filter(.summary, assessment == 'blame' &
experimental_situation == 'nonagentive') %>% pull(stdev)`).
Comparing the level of blame assessed by the two groups, we obtain a t-test
that is significant at the .05 level
($\Delta_{ag-nonag} = `r t_blame$estimate[1] - t_blame$estimate[2]`,
t(`r t_blame$parameter`) = `r t_blame$statistic`,
p = `r t_blame$p.value`,
95\% \text{CI} = [`r t_blame$conf.int[1]`, `r t_blame$conf.int[2]`]$)

## Study 2a

```{r s2a-load-data}
source(here::here('analyses',
                  'study_2a',
                  'wrangling',
                  'study_2a_prepare-analysis-data.R'))
```

```{r s2a-plot-assessments, fig.cap='Individual responses to the proposed fine and stated level of blame (jittered horizontally). The large markers represent each group\'s mean value.'}
.summary <- dplyr::group_by(d_s2a,
                            agency,
                            blame_level) %>%
    dplyr::summarise(.,
                     m = mean(assess_fine),
                     stdev = sd(assess_fine))

s2Plot(d_s2a,
       .summary)
```

```{r s2a-anova}
anova_active <- aov(lm(assess_active_role ~ agency * blame_level,
                       d_s2a)) %>%
    summary(.)

anova_active <- anova_active[[1]]

rownames(anova_active) <- trimws(rownames(anova_active))

anova_fine <- aov(lm(assess_fine ~ agency * blame_level,
                     d_s2a)) %>%
    summary(.)

anova_fine <- anova_fine[[1]]

rownames(anova_fine) <- trimws(rownames(anova_fine))
```

```{r s2a-table}
.summary <- dplyr::group_by(d_s2a,
                            agency,
                            blame_level) %>%
    dplyr::summarize(.,
                     'm_fine' = mean(assess_fine),
                     'stdev_fine' = sd(assess_fine),
                     'm_activity' = mean(assess_active_role,
                                         na.rm = T),
                     'stdev_activity' = sd(assess_active_role,
                                           na.rm = T))

s2Table(.summary)
```

The groups formed by different combinations of agency and stated level of blame
were compared using independent-samples two-way ANOVAs. As in Studies 1a and 1b,
there was a manipulation check asking the participants to rate to which extent
the subject of the described event played an active role in starting the fire.

Comparing the participants' assessment of the subject's activity, we find
a nonsignificant effect of agency
($F(`r anova_active[rownames(anova_active) == 'agency', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'agency', 'F value']`,
p = `r anova_active[rownames(anova_active) == 'agency', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'agency')`$),
a significant effect of assigned level of blame
($F(`r anova_active[rownames(anova_active) == 'blame_level', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'blame_level', 'F value']`,
p =
`r anova_active[rownames(anova_active) == 'blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'blame_level')`$),
and a nonsignificant interaction
($F(`r anova_active[rownames(anova_active) == 'agency:blame_level', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'agency:blame_level', 'F value']`,
p = `r anova_active[rownames(anova_active) == 'agency:blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'agency:blame_level')`$).

Comparing the participants' assigned fines, we find
a nonsignificant effect of agency
($F(`r anova_fine[rownames(anova_fine) == 'agency', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'agency', 'F value']`,
p = `r anova_fine[rownames(anova_fine) == 'agency', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'agency')`$),
a significant effect of assigned level of blame
($F(`r anova_fine[rownames(anova_fine) == 'blame_level', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'blame_level', 'F value']`,
p =
`r anova_fine[rownames(anova_fine) == 'blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'blame_level')`$),
and a nonsignificant interaction
($F(`r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'F value']`,
p = `r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'agency:blame_level')`$),

## Study 2b

```{r s2b-load-data}
source(here::here('analyses',
                  'study_2b',
                  'wrangling',
                  'study_2b_prepare-analysis-data.R'))
```

```{r s2b-plot-assessments, fig.cap='Individual responses to the proposed fine and stated level of blame (jittered horizontally). The large markers represent each group\'s mean value.'}
.summary <- dplyr::group_by(d_s2b,
                            agency,
                            blame_level) %>%
    dplyr::summarise(.,
                     m = mean(assess_fine),
                     stdev = sd(assess_fine))

s2Plot(d_s2b,
       .summary)
```

```{r s2b-anova}
anova_active <- aov(lm(assess_active_role ~ agency * blame_level,
                       d_s2b)) %>%
    summary(.)

anova_active <- anova_active[[1]]

rownames(anova_active) <- trimws(rownames(anova_active))

anova_fine <- aov(lm(assess_fine ~ agency * blame_level,
                     d_s2b)) %>%
    summary(.)

anova_fine <- anova_fine[[1]]

rownames(anova_fine) <- trimws(rownames(anova_fine))
```

The groups formed by different combinations of agency and stated level of blame
were compared using independent-samples two-way ANOVAs. As in Studies 1a and 1b,
there was a manipulation check asking the participants to rate to which extent
the subject of the described event played an active role in starting the fire.

```{r s2b-table}
.summary <- dplyr::group_by(d_s2b,
                            agency,
                            blame_level) %>%
    dplyr::summarize(.,
                     'm_fine' = mean(assess_fine),
                     'stdev_fine' = sd(assess_fine),
                     'm_activity' = mean(assess_active_role,
                                         na.rm = T),
                     'stdev_activity' = sd(assess_active_role,
                                           na.rm = T))

s2Table(.summary)
```

Comparing the participants' assessment of the subject's activity, we find
a significant effect of agency
($F(`r anova_active[rownames(anova_active) == 'agency', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'agency', 'F value']`,
p = `r anova_active[rownames(anova_active) == 'agency', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'agency')`$),
a significant effect of assigned level of blame
($F(`r anova_active[rownames(anova_active) == 'blame_level', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'blame_level', 'F value']`,
p =
`r anova_active[rownames(anova_active) == 'blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'blame_level')`$),
and a nonsignificant interaction
($F(`r anova_active[rownames(anova_active) == 'agency:blame_level', 'Df']`,
`r anova_active[rownames(anova_active) == 'Residuals', 'Df']`) =
`r anova_active[rownames(anova_active) == 'agency:blame_level', 'F value']`,
p = `r anova_active[rownames(anova_active) == 'agency:blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_active, 'agency:blame_level')`$).

Comparing the participants' assigned fines, we find
a significant effect of agency
($F(`r anova_fine[rownames(anova_fine) == 'agency', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'agency', 'F value']`,
p = `r anova_fine[rownames(anova_fine) == 'agency', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'agency')`$),
a significant effect of assigned level of blame
($F(`r anova_fine[rownames(anova_fine) == 'blame_level', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'blame_level', 'F value']`,
p =
`r anova_fine[rownames(anova_fine) == 'blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'blame_level')`$),
and a nonsignificant interaction
($F(`r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'Df']`,
`r anova_fine[rownames(anova_fine) == 'Residuals', 'Df']`) =
`r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'F value']`,
p = `r anova_fine[rownames(anova_fine) == 'agency:blame_level', 'Pr(>F)']`,
\eta^2 = `r getEtaSquared(anova_fine, 'agency:blame_level')`$),
